Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
evaluation

For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (Disco, QB, SKOS, PHDD, DCAT, XKOS) and classify them according to the complexity level of their type and their severity level. For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints. 
Based on the results, we formulate several hypotheses to direct the further development of constraint langugaes.

@@

In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the dataset descriptions and in the case that it matters for the purpose of this paper.\tb{hab ich eingefügt, ist der absatz von dir...}

@@

\ke{in guter tradition unserer arbeitsgruppe würde ich mich als senior researcher um die einleitung kümmern, die gefällt mir so nicht}\tb{sehr gerne}

@@

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
In close collaboration with several \emph{SBE} domain experts, we defined 246 constraint 
of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level. 
For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
We distinct two classes of vocabularies: 
(1) well-established vocabularies (e.g., \emph{QB}, \emph{SKOS}) which are widely adopted and accepted and 
(2) newly developed vocabularies (e.g., \emph{Disco} which will be published in 2015) which are either recently published or are still in the publication process.
%It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
%and that early adopters did not properly understand its formal specification.
Based on this evaluation we formulate hypotheses.
Nevertheless, we have to be careful making general statements for all vocabularies 
as these hypotheses still have to be verified or falsified in terms of future work 
by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
\ke{das ist zu früh finde um schon einzuschränken, erst mal ergebnisse, dann hypothesen, dann kritische auseinandersetzung}

@@

>>>>

For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (Disco, QB, SKOS, PHDD, DCAT, XKOS) and classify them according to the complexity level of their type and their severity level. For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints. 
Based on the results, we formulate several hypotheses to direct the further development of constraint languages.

@@

In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.

@@

@@

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
In close collaboration with several \emph{SBE} domain experts, we defined 246 constraint 
of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level. 
For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
We distinct two classes of vocabularies: 
(1) well-established vocabularies (e.g., \emph{QB}, \emph{SKOS}) which are widely adopted and accepted and 
(2) newly developed vocabularies (e.g., \emph{Disco} which will be published in 2015) which are either recently published or are still in the publication process.
%It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
%and that early adopters did not properly understand its formal specification.
\ke{ergebnisse, dann hypothesen, dann kritische auseinandersetzung}

@@

Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
Nevertheless, we have to be careful making general statements for all vocabularies 
as these hypotheses still have to be verified or falsified in terms of future work 
by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
